TG2 Publications

### 2025-08-18 papers.qmd
Added DOI (or other link) for books

* Harrell FE. Regression Modeling Strategies: With Applications to Linear Models, Logistic Regression, and Survival Analysis. Springer: New York, 2015. <br> *Integrates statistical rigor with practical guidance on variable selection, model specification, and validation across a range of regression contexts*.

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008. <br> *Presents a structured approach to modeling continuous variables using fractional polynomials, with an emphasis on reproducibility and clinical relevance*.

* Wood S. Generalized Additive Models. Chapman & Hall/CRC: New York, 2006. <br> *Offers an accessible yet thorough treatment of additive modeling techniques for capturing nonlinear relationships in multivariable settings*.

* Miller A. Subset Selection in Regression. Taylor & Francis: Boca Raton, Florida, 2002. <br> *Provides a critical examination of subset selection methods, discussing their statistical properties, limitations, and applications*.

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001. <br> *Covers spline-based methods in detail, offering practical advice for incorporating flexible functional forms into regression models*.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990. <br> *Introduces foundational concepts in additive modeling, balancing statistical theory with illustrative applied examples*.

>>>>

* Harrell FE. Regression Modeling Strategies: With Applications to Linear Models, Logistic Regression, and Survival Analysis. Springer: New York, 2015. [https://doi.org/10.1007/978-3-319-19425-7](https://doi.org/10.1007/978-3-319-19425-7)
<br> *Integrates statistical rigor with practical guidance on variable selection, model specification, and validation across a range of regression contexts*.

* Royston P, Sauerbrei W. Multivariable model-building: a pragmatic approach to regression analysis based on fractional polynomials for modelling continuous variables. John Wiley & Sons; 2008. [https://www.wiley.com/en-us/Multivariable+Model+-+Building%3A+A+Pragmatic+Approach+to+Regression+Anaylsis+based+on+Fractional+Polynomials+for+Modelling+Continuous+Variables-p-9780470028421](Link)
<br> *Presents a structured approach to modeling continuous variables using fractional polynomials, with an emphasis on reproducibility and clinical relevance*.

* Wood S. Generalized Additive Models. Chapman & Hall/CRC: New York, 2006. [https://doi.org/10.1201/9781315370279](https://doi.org/10.1201/9781315370279)
<br> *Offers an accessible yet thorough treatment of additive modeling techniques for capturing nonlinear relationships in multivariable settings*.

* Miller A. Subset Selection in Regression. Taylor & Francis: Boca Raton, Florida, 2002. [https://doi.org/10.1201/9781420035933](https://doi.org/10.1201/9781420035933)
<br> *Provides a critical examination of subset selection methods, discussing their statistical properties, limitations, and applications*.

* Boer C de. A Practical Guide to Splines revised edn. Springer: New York, 2001. [https://link.springer.com/book/9780387953663](Link)
<br> *Covers spline-based methods in detail, offering practical advice for incorporating flexible functional forms into regression models*.

* Hastie T, Tibshirani R.. Generalized Additive Models. Chapman & Hall/CRC: New York, 1990. [https://www.routledge.com/Generalized-Additive-Models/Hastie-Tibshirani/p/book/9780412343902](Link)
<br> *Introduces foundational concepts in additive modeling, balancing statistical theory with illustrative applied examples*.
